---
title: "NYCAASC_Pilot_Analysis"
author: "Amelia Chu"
date: "November 19, 2015"
output: html_document
---

NYCAASC Pilot Analysis
------
Loading Libraries:
```{r setup, cache=FALSE, echo=FALSE}
library(stringr)
```

Reading Data:
```{r}
data <- read.csv("/Users/ameliachu/Dropbox/NYCAASC_Pilot_Quant_CLEAN.csv")
```

Creating Dummy Variables for whatInfo responses:
```{r}
data$whatInfo_learn <- str_detect(as.character(data$whatInfo),"Learn about History of NYCAASC")

data$whatInfo_learnHist <- str_detect(as.character(data$whatInfo),"Learn about History of NYCAASC")

data$whatInfo_learnChair <- str_detect(as.character(data$whatInfo),"To Learn About NYCAASC Directors and Chairs")

data$whatInfo_apply <- str_detect(as.character(data$whatInfo),"To Apply for Committee Membership")

data$whatInfo_ahm <- str_detect(as.character(data$whatInfo),"Information on AHM (Asian Heritage Month)")

data$whatInfo_mistake <- str_detect(as.character(data$whatInfo),"I came upon the website by mistake")

data$whatInfo_general <- str_detect(as.character(data$whatInfo),"General Information about NYCAASC")
```
No significant differences in  ability to find information, perceived ease of use or perceived aesthetic appeal, in terms of what information participants were seeking.

Distribution of Members by School:
```{r}
summary(data$school)
```

```{r}
summary(data$easeInfo)
summary(data$findInfo)
sd(data$easeInfo, na.rm=TRUE)
sd(data$findInfo, na.rm=TRUE)
summary(data$prettyWeb)
sd(data$prettyWeb, na.rm=TRUE)

```

No significant relationship between percieved ease of use and perceived aesthetic appeal.

Close to significant relationship between perceived ease of use and ability to find information (p = .062).

```{r}
linear <- lm(easeInfo ~ findInfo, data)
summary(linear)
```

^easeInfo = 5.23 - 0.7689findInfo + 0.3472prettyweb
There is statistically significant evidence that this model is useful in predicting easeInfo (p=0.04037).
Maybe percieved easeInfo

```{r}
linear <- lm(easeInfo ~ findInfo + prettyWeb, data)
summary(linear)
```

No significant differences between frequency of visits and perceived ease of use. 
No significant differences between frequency of visits and ability to find information. 
Significant difference between frequency of visits and perceived aesthetic appeal (p = .0251). 

```{r}
summary(data$prettyWeb)
summary(data$visitFreq)
fit <- aov(prettyWeb ~ visitFreq, data = data)
summary(fit)
boxplot(prettyWeb ~ visitFreq, data = data, horizontal = TRUE)
```

```{r}
data$school2 <- ifelse((str_detect(as.character(data$school), fixed("High School"))), "highschool", "college")
school <- as.factor(data$school2)
data$schoolLevel <-  school : data$yearSchool
```

Close to significant difference in perceived aesthetic appeal in terms of year in school (p = 0.0874).

```{r}
summary(data$schoolLevel)
fit <- aov(prettyWeb ~ schoolLevel, data = data)
summary(fit)
```

Significant difference in perceived ease of use in terms of year in school (p = 0.0379).
```{r}
fit <- aov(easeInfo ~ schoolLevel, data = data)
summary(fit)

boxplot(easeInfo ~ schoolLevel, data = data, horizontal = TRUE)
```

Close to significant difference in ability to find information in terms of year in school (p = 0.0874).
```{r}
fit <- aov(findInfo ~ schoolLevel, data = data)
summary(fit)
```

No significant differences in ability to find information, perceived ease of use, or perceived aesthetic appeal, in terms of how participant learned of NYCAASC. 

```{r}
data$findConf2 <- ifelse((str_detect(as.character(data$findConf), fixed("Pong"))), "Pong", ifelse((str_detect(as.character(data$findConf), fixed("NYCAASC website"))), "NYCAASC website", ifelse((str_detect(as.character(data$findConf), fixed("NYU Clubfest"))), "NYU Clubfest", ifelse((str_detect(as.character(data$findConf), fixed("AHM Email"))), "AHM Email", ifelse((str_detect(as.character(data$findConf), fixed("NYCAASC Flyer"))), "NYCAASC Flyer", " Other Human Referral")))))

summary(as.factor(data$findConf2))
#data$findConf2 No significance, but at least I know how to do this now... TT-TT

```

